An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/abs.tex
config: abs and intro
config: abs

\app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors. 
Our experiment shows \app is able to detect 83\% errors from
a real-world dataset with 261 incorrect MySQL configuration files.

>>>>

\app is capable of detecting various errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
and entry missing errors. 
We evaluate \app using a real-world dataset with 261 incorrect 
MySQL configuration files,
and \app is able to correctly 
detect errors (previous work failed to
detect) in 217 files.
